\Title

### 2016-10-05 manuscript/manuscript.tex
Fixes reference to bird20013
Had an extra "a" in the citation tag

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-moho}
    \caption{
        The estimated Moho depth of South America.
        Dotted lines represent the boundaries between major geologic provinces
        \citep[after][]{assumpcao2013a, goutorbe2015};
        AD: Andean Province,
        AFB: Andean foreland basins,
        AM: Amazonas Basin,
        BR: Brazilian Shield,
        BO: Borborema province,
        CH: Chaco Basin,
        GB: Guyana Basin,
        GU: Guyana Shield,
        PB: Parnaíba Basin,
        PC: Parecis Basin,
        PR: Paraná Basin,
        PT: Patagonia province,
        SF: São Francisco Craton,
        SM: Solimões Basin.
        Solid orange lines mark the limits of the main lithospheric plates
        \citep{bird2003a};
        AF: Africa Plate,
        AN: Antarctica Plate,
        CA: Caribbean Plate,
        CO: Cocos Plate,
        SA: South America Plate,
        SC: Scotia Plate,
        NZ: Nazca Plate.
        The solid light grey line is the 35 km Moho depth contour.
    }
    \label{fig:sam-moho}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/south-america-moho}
    \caption{
        The estimated Moho depth of South America.
        Dotted lines represent the boundaries between major geologic provinces
        \citep[after][]{assumpcao2013a, goutorbe2015};
        AD: Andean Province,
        AFB: Andean foreland basins,
        AM: Amazonas Basin,
        BR: Brazilian Shield,
        BO: Borborema province,
        CH: Chaco Basin,
        GB: Guyana Basin,
        GU: Guyana Shield,
        PB: Parnaíba Basin,
        PC: Parecis Basin,
        PR: Paraná Basin,
        PT: Patagonia province,
        SF: São Francisco Craton,
        SM: Solimões Basin.
        Solid orange lines mark the limits of the main lithospheric plates
        \citep{bird2003};
        AF: Africa Plate,
        AN: Antarctica Plate,
        CA: Caribbean Plate,
        CO: Cocos Plate,
        SA: South America Plate,
        SC: Scotia Plate,
        NZ: Nazca Plate.
        The solid light grey line is the 35 km Moho depth contour.
    }
    \label{fig:sam-moho}
\end{figure*}
